### 2025-09-30 README.Rmd
cleaning

Dependency on `cmdstanr:`

Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

Install `localHierarchy` from Github:
`remotes::install_github("AlkemaLab/localhierarchy")`

>>>>

-   Dependency on `cmdstanr:` Instructions for installing `cmdstanr` are available in their [Getting started](https://mc-stan.org/cmdstanr/articles/cmdstanr.html) guide.

-   Install `localHierarchy` from Github: `remotes::install_github("AlkemaLab/localhierarchy")`
